Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-03 paper.tex
Added slicing measurements for desktop
Added labels for performance charts so they can be referenced
Reference performance charts in text

\begin{table}
  \centering
  \begin{tabular}{ l l l }
    \toprule
    Approach & Macbook & Desktop \\
    \midrule
    Boolean AND with masking & 22 & 13 \\
    Boolean AND with XOR & 24 & 13 \\
    Slicing & 6 & ? \\
    Optimized Slicing & 25 & ? \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

% Furthermore, a variety of sampling rates were used to determine how each
% approach scales as the number of samples taken increases.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=2.2 GHz i7 with AMD Radeon HD 6750M,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz P4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 10)
  (200, 6)
  (300, 4)
  (400, 3)
  (500, 2)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 13)
  (200, 7)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 18)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 15)
  (200, 8)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  Here the
slicing with uniforms method is fastest, followed by the slicing with attributes
method, and the Boolean XOR method.  The depth-masking method is slowest.
}
\end{figure}

>>>>

\begin{table}
  \centering
  \begin{tabular}{ l l l }
    \toprule
    Approach & Macbook & Desktop \\
    \midrule
    Boolean AND with masking & 22 & 13 \\
    Boolean AND with XOR & 24 & 13 \\
    Slicing & 6 & 18 \\
    Optimized Slicing & 25 & 15 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

Furthermore, a variety of sampling rates were used to determine how each
approach scales as the number of samples taken increases.  Figure
\ref{macbook-performance-chart} shows how the methods scale on a 2.2 GHz Intel
Core i7 Macbook Pro with an AMD Radeon HD 6750M video card.  Likewise figure
\ref{desktop-performance-chart} does so for an older 3.0 GHz Intel Pentium 4
Linux desktop with an NVIDIA GeForce 8500 GT video card.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=2.2 GHz i7 with AMD Radeon HD 6750M,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\label{macbook-performance-chart}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz P4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 10)
  (200, 6)
  (300, 4)
  (400, 3)
  (500, 2)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 13)
  (200, 7)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 18)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 15)
  (200, 8)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  Here the
slicing with uniforms method is fastest, followed by the slicing with attributes
method, and the Boolean XOR method.  The depth-masking method is slowest.
}
\label{desktop-performance-chart}
\end{figure}
